\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-09-20 paper/manuscript.tex
multiple changes to incorporate cross-city entropy, experimenting with mallet parameters, top words through aggregated topics, etc.
added some basic descriptive statistics of documents by party; because this keeps coming up
a few additions to the paper (STM and SVM) + scripts for those + elasticnet

@@

@@

@@

>>>>

$T_{1}+\beta_1$

@@

\subsubsection{LDA diagnostics}

@@

\subsubsection{Structural topic model}
An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics. This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}. However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem. Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic. Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose. The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to. Interestingly the same is true for a number of the cities as well. The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.

\subsubsection{Prediction with SVM}
An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party. Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context. Here, we rely on SVM, through three different implementations. The SciKitLearn package in Python, the e1071 package as well as the mlr package (relying on the kernlab package) in R. Predicting based on the document-term matrix (either in its regular form, or as its tf-idf representation), and using five-fold cros-validation, SciKitLearn produces a predictive accuracy of at most 78\%. Parameter tuning did not lead to any improvements. The e1071 package in R, relying on the top 5000 features ranked through tf-idf fared slightly better, at 82 percent correctly predicted. Finally, the mlr/kernlab implementation (as well as the e1071 implementation through mlr) has not worked at all so far, resulting in stack overflow errors (which appears to be due to memory limitations in R).

Another point worth noting is that \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.

@@

%stm results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic. This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
	\label{stm_results}
	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
\end{figure}

%Partisan top words
\input{tables/partisanTopWords.tex}

%Some basic descriptive statistics of documents by party
\input{tables/descriptiveStatisticsPartisan.tex}
